---
title: "Note For Using Python on a MacBook Pro"
author: "Rob Donald"
subtitle: "Research Running Log"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
header-includes:
- \usepackage{graphicx}
output:
  pdf_document:
    fig_caption: yes
    toc: yes
    toc_depth: '2'
urlcolor: blue
---
\def\shrug{\texttt{\raisebox{0.75em}{\char`\_}\char`\\\char`\_\kern-0.5ex(\kern-0.25ex\raisebox{0.25ex}
{\rotatebox{45}{\raisebox{-.75ex}"\kern-1.5ex\rotatebox{-90})}}\kern-0.5ex)\kern-0.5ex\char`\_/\raisebox{0.75em}
{\char`\_}}}

```{r setup, include=FALSE}
# The above LaTex
# From https://tex.stackexchange.com/questions/279100/typeset-the-shrug-%C2%AF-%E3%83%84-%C2%AF-emoji (post by Mark Wibrow)
# The fig.pos = 'h' tells LaTeX to put the figure where you ask for it
knitr::opts_chunk$set(echo = TRUE,fig.height=8,fig.width=12,fig.pos = 'h')
options(width=80)
```

```{r library_setup, include=FALSE}
suppressMessages({suppressWarnings({
    library(dplyr)
    library(readr)
    library(lubridate)
    library(here)
    
    library(ggplot2)
    library(RobsRUtils)
    library(pander)
    library(kableExtra)

})})
```

# Abstract

A set of notes documenting the initially painful process of getting a Python development environment up and running
on my MacBook Pro (Retina, 13-inch, Early 2013, macOS Catalina, 10.15.7). 

This is written from a point of view of having used R for the last 5 years plus. But with a previous background of using
Python 2.x very heavily.


# 2021-11-20

* Initial installation of Python 3.x using Homebrew

* Initial playing with VS Code.


# 2021-11-21

## Rmarkdown for Python?

I thought I'd check if there was a Python equivalent to Rmarkdown and in particular Rmarkdown to PDF.

Using this Google query "Does python have an equivalent to Rmarkdown", the answer appears to be ... No.

See (https://jackbakerds.com/posts/python-equivalent-rmarkdown/)





