---
title: "Note For Using Python on a MacBook Pro"
author: "Rob Donald"
subtitle: "Research Running Log"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
header-includes:
- \usepackage{graphicx}
output:
  pdf_document:
    fig_caption: yes
    toc: yes
    toc_depth: '2'
urlcolor: blue
---
\def\shrug{\texttt{\raisebox{0.75em}{\char`\_}\char`\\\char`\_\kern-0.5ex(\kern-0.25ex\raisebox{0.25ex}
{\rotatebox{45}{\raisebox{-.75ex}"\kern-1.5ex\rotatebox{-90})}}\kern-0.5ex)\kern-0.5ex\char`\_/\raisebox{0.75em}
{\char`\_}}}

```{r setup, include=FALSE}
# The above LaTex
# From https://tex.stackexchange.com/questions/279100/typeset-the-shrug-%C2%AF-%E3%83%84-%C2%AF-emoji (post by Mark Wibrow)
# The fig.pos = 'h' tells LaTeX to put the figure where you ask for it
knitr::opts_chunk$set(echo = TRUE,fig.height=8,fig.width=12,fig.pos = 'h')
options(width=80)
```

```{r library_setup, include=FALSE}
suppressMessages({suppressWarnings({
    library(dplyr)
    library(readr)
    library(lubridate)
    library(here)
    
    library(ggplot2)
    library(RobsRUtils)
    library(pander)
    library(kableExtra)

})})
```

# Abstract

A set of notes documenting the initially painful process of getting a Python development environment up and running
on my MacBook Pro (Retina, 13-inch, Early 2013, macOS Catalina, 10.15.7). 

This is written from a point of view of having used R for the last 5 years plus. But with a previous background of using
Python 2.x very heavily.


# 2021-11-20

* Initial installation of Python 3.x using Homebrew

* Initial playing with VS Code.

* Problems accessing Photos DB from within VS Code debug to console. I've tracked this
down to some clash of macosx Catalina security settings. If you run the code from a terminal
it has access no problem because I've allowed that in the System Settings.

Workaround to use project settings (.vscode/launch.json) of

* "console": "externalTerminal"



# 2021-11-21

## Rmarkdown for Python?

I thought I'd check if there was a Python equivalent to Rmarkdown and in particular Rmarkdown to PDF.

Using this Google query "Does python have an equivalent to Rmarkdown", the answer appears to be ... No.

See (https://jackbakerds.com/posts/python-equivalent-rmarkdown/)


# 2021-11-24

More observations on using VS Code with Python. It seems to me at this stage to be pretty
awkward to use. It's full of, for me, irritating modes which I accept, particularly
at this stage, are due to my dislike of using Python because it still seems to be
very nerdy to set up. This coupled with what seems to still be a less than mature
IDE means there is a lot of gritting of teeth.

Another issue is that a lot of the stackoverflow answers don't work because they are
suggesting fixes which are in earlier (and I suspect more buggy) versions.

The one I'm dealing with tonight is that when you start a project it seems to automatically
run the virtual environment and then *all* the code in the file you have open. 

In my case because of the problem of the console not having the right security setup to access
the Photos DB this causes an immediate crash. I *know* that will happen and it *is* annoying
and had to be solved by using the external terminal. See the entry for 2021-11-20.

By 20:55 some progress on extraction techniques. I accept that I need to make allowances
for re-learning the Python basics *and* a new IDE.

# Install pip-date

* See (https://stackoverflow.com/questions/30559214/get-date-and-time-of-installation-for-packages-installed-via-pip)

This was installed into the venv for this project.

# VS Code Things

Multi-root workspaces. This just means having access to more than one folder in your "project". 
The problem is that they can't use the word "project" because it means other things in closed source
Visual Studio IDE product. See (https://code.visualstudio.com/docs/editor/workspaces).




